Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-20 notes.tex
updated the self energy part

@@

@@

			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]

@@

	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\

@@

\subsection{Calculation of self energy matrix from the Dyson equation}
% Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
% \begin{eqnarray}
% \Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
% &=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
% \end{eqnarray}
% This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
% \begin{equation}\begin{aligned}
% 	\label{selfenergy}
% 	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
% \end{aligned}\end{equation}
With the knowledge of the momentum-space Greens function $G_H(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_H(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
\end{aligned}\end{equation}

@@

\subsection{On the Bethe lattice}
Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality). Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite. This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well. Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements). We can also see this from eqs.\eqref{local_gf},\eqref{nn_gf} where $(G^{H})^{-1}$ matrix has no $k$ dependence as $(G^{H})^{-1}_{ij}\propto 1/w \to 0$ as $w\to\infty$. Thus, in the self-energy 
\begin{eqnarray}
\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}\nonumber\\
&\to & \lim_{w\to\infty} \omega - {g}_{0} + t^{H}\xi_{\vec{k}}~,
\end{eqnarray}
We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.

>>>>

	\label{G_mat_loc}

@@

	\label{G_mat_nn}

@@

			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]

@@

	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\

@@

\subsection{Calculation of self energy matrix from the Dyson equation}
% Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
% \begin{eqnarray}
% \Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
% &=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
% \end{eqnarray}
% This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
% \begin{equation}\begin{aligned}
% 	\label{selfenergy}
% 	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
% \end{aligned}\end{equation}
With the knowledge of the momentum-space Greens function $G_H(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_H(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
\end{aligned}\end{equation}

@@

\subsection{On the Bethe lattice}
Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality). Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite. This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well. Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements). We can also see this from eqs.\eqref{G_mat_nn}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
\begin{equation}\begin{aligned}
	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma \to 0
\end{aligned}\end{equation}
There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself. This result then implies that $G^{H}$ matrix has no $k$ dependence. 
\\\\
In this limit, the self-energy also simplifies:
\begin{equation}\begin{aligned}
	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
\end{aligned}\end{equation}
We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
